### 2016-08-12 docs/ms_communitySynchrony.Rmd
submission version for Ecology

---
bibliography: ~/Dropbox/Bibliography/CommunitySynchrony.bib
csl: components/ecology.csl
fontsize: 12pt
geometry: margin=1in
header-includes:
- \usepackage{lineno}
- \linenumbers
- \usepackage{setspace}
- \usepackage{todonotes}
- \doublespacing
- \usepackage{rotating}
- \usepackage{color, soul}
layout: 12pt
linkcolor: black
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
urlcolor: black
---

<!--    - \usepackage{times} 
   - \usepackage[document]{ragged2e} -->

@@

INTRODUCTION
------------
Ecosystems are being transformed by species extinctions [@Cardinale2012], changes in community composition [@Dornelas2014a; @Vellend2013], and anthropogenic environmental change [@Vitousek1997], impacting the provisioning and stability of ecosystem services [@Loreau2001a; @Hooper2005; @Rockstrom2009].
Experiments have provided compelling evidence that decreases in species richness will decrease productivity [@Tilman2001] and the temporal stability of productivity [@Tilman2006; @Hector2010].
The stabilizing effect of species richness stems from individual species responding in different way} to environmental fluctuations (environmental stochasticity), or fluctuating asynchronously because of random chance events (demographic stochasticity) [@Hector2010; @Isbell2009; @DeMazancourt2013a].
Species richness affects synchrony because larger species pools are more likely to contain species that respond disimilarly to environmental conditions [@Yachi1999], implying that species losses will reduce ecosystem stability.
Even without species losses, abiotic homogenization can weaken compensatory dynamics and, in turn, decrease temporal stability of ecosystem functioning [@Hautier2014].
The link between synchrony and stability means that a mechanistic understanding of synchrony can help us predict the impacts of global change on ecosystem stability.

@@

THEORETICAL MODEL
-----------------
### The model
While existing theory has identified the factors driving synchrony, we do not have a simple expression to predict synchrony in a particular community with all factors operating simultaneously. 
However, we can derive analytical predictions for species synchrony under special limiting cases.
The limiting case predictions we derive serve as baselines to help us interpret results from empirically-based simulations (described below).
We focus on synchrony of per capita growth rates, rather than abundances, because growth rates represent the instantaneous response of species to the environment and competition, and are less susceptible to the legacy effects of drift and disturbance [@Loreau2008a].
We present equivalent results for synchrony of species abundances in the Online Supporting Information, and show that they lead to the same overall conclusions as synchrony of per capita growth rates.
Following @Loreau2008a and @DeMazancourt2013a, we define population growth, ignoring observation error, as

@@

\noindent where $N_i(t)$ is the biomass of species *i* in year *t*, and $r_i(t)$ is its population growth rate in year *t*. 
$r_{mi}$ is species *i*'s intrinsic rate of increase, $K_i$ is its carrying capacity, and $\alpha_{ij}$ is the interspecific competition coefficient representing the effect of species *j* on species *i*. 
Environmental stochasticity is incorporated as $\sigma_{ei}u_{ei}(t)$, where $\sigma_{ei}^2$ is the environmental variance and $u_{ei}$ are normal random variables with zero mean and unit variance that are independent through time but may be correlated between species.
Demographic stochasticity arises from variations in births and deaths among individuals (e.g., same states, different fates), and is included in the model as a first-order, normal approximation [@Lande2003; @DeMazancourt2013a].
$\sigma_{di}^2$ is the demographic variance and $u_{di}(t)$ are independent normal variables with zero mean and unit variance.
To derive analytical predictions we solved a first-order approximation of Equation 2 [@DeMazancourt2013a and Online Supporting Information].
Due to the linear approximation approach, our analytical predictions will likely fail in communities where species exhibit large fluctuations due to limit cycles and chaos [@Loreau2008a].
Indeed, one of the advantages of focusing on growth rates rather than abundances is that growth rates are more likely to be well-regulated around an equilibrium value, if the long-term average of a species' growth rate is relatively small (e.g., $r < 2$).

@@

#### Fitting statistical models
Vital rate regressions are the building blocks of our dynamic models: an integral projection model (IPM) and an individual-based model (IBM).
We followed the approach of @Chu2015 to fit statistical models for survival, growth, and recruitment (see Online Supporting Information for full details).
We modeled survival probability of each genet as function of genet size, temporal variation among years, permanent spatial variation among groups of quadrats, and local neighborhood crowding from conspecific and heterospecific genets.
Regression coefficients for the effect of crowding by each species can be considered a matrix of interaction coefficients whose diagonals represent intraspecific interactions and whose off-diagonals represent interspecific interactions [@Adler2010]. These interaction coefficients can take positive (facilitative) or negative (competitive) values.
We modeled growth as the change in size of a genet from one year to the next, which depends on the same factors as the survival model.
We fit the survival and growth regressions using INLA [@Rue2014], a statistical package for fitting generalized linear mixed effects models via approximate Bayesian inference [@Rue2009], in R [@R2013].
Crowding was treated as a fixed effect without a temporal component because most 95\% credible intervals for random year effects on crowding broadly overlapped zero and, in a test case, including yearly crowding effects did not change our results.
Spatial (quadrat groupings) variation was treated as a random effect on the intercept and temporal (interannual) variation was treated as random effects on the intercept and the effect of genet size in the previous year (Online Supporting Information).

@@

For all five communities, the synchrony of species' growth rates when growing in isolation almost perfectly matched species synchrony in polyculture (Fig. 3).
Results for synchrony of percent cover are qualitatively similar, but simulation results were more variable and less consistent with analytical predictions and observed synchrony (Online Supporting Information, Figs. S2-S3).

DISCUSSION
----------
Our study produced four main findings that were generally consistent across five natural plant communities: (1) limiting-case predictions from the theoretical model were well-supported by simulations from the empirical models; (2) demographic stochasticity decreased community synchrony, as expected by theory, and its effect was largest in small populations; (3) environmental fluctuations increased community synchrony relative to simulations in constant environments because species-specific responses to the environment were positively, though not perfectly, correlated; and (4) interspecific interactions were weak and therefore had little impact on community synchrony.
We also found that analyses based on synchrony of species' percent cover, rather than growth rates, were uninformative (Figs. S2-S3) since the linear approximation required for analytical predictions is a stronger assumption for abundance than growth rates, especially given relatively short time-series (Online Supporting Information).
Thus, our results provide further evidence that it is difficult to decipher mechanisms of species synchrony from abundance time series, as expected by theory [@Loreau2008a].
Observed synchrony of per capita growth rates was positively correlated with the variability of percent cover across our focal communities, which confirms that we are investigating an important process underlying ecosystem stability.

>>>>

---
bibliography: ~/Dropbox/Bibliography/CommunitySynchrony.bib
csl: components/ecology.csl
fontsize: 12pt
geometry: margin=1in
header-includes:
- \usepackage{lineno}
- \linenumbers
- \usepackage{setspace}
- \usepackage{todonotes}
- \doublespacing
- \usepackage{rotating}
- \usepackage{color, soul}
- \usepackage{times} 
- \usepackage[document]{ragged2e}
layout: 12pt
linkcolor: black
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
urlcolor: black
---

\renewcommand\linenumberfont{\normalfont\tiny\sffamily\color{gray}}

<!--    
    -->

@@

INTRODUCTION
------------
Ecosystems are being transformed by species extinctions [@Cardinale2012], changes in community composition [@Dornelas2014a; @Vellend2013], and anthropogenic environmental change [@Vitousek1997], impacting the provisioning and stability of ecosystem services [@Loreau2001a; @Hooper2005; @Rockstrom2009].
Experiments have provided compelling evidence that decreases in species richness will decrease productivity [@Tilman2001] and the temporal stability of productivity [@Tilman2006; @Hector2010].
The stabilizing effect of species richness stems from individual species responding in different ways to environmental fluctuations (environmental stochasticity), or fluctuating asynchronously because of random chance events (demographic stochasticity) [@Hector2010; @Isbell2009; @DeMazancourt2013a].
Species richness affects synchrony because larger species pools are more likely to contain species that respond disimilarly to environmental conditions [@Yachi1999], implying that species losses will reduce ecosystem stability.
Even without species losses, abiotic homogenization can weaken compensatory dynamics and, in turn, decrease temporal stability of ecosystem functioning [@Hautier2014].
The link between synchrony and stability means that a mechanistic understanding of synchrony can help us predict the impacts of global change on ecosystem stability.

@@

THEORETICAL MODEL
-----------------
### The model
While existing theory has identified the factors driving synchrony, we do not have a simple expression to predict synchrony in a particular community with all factors operating simultaneously. 
However, we can derive analytical predictions for species synchrony under special limiting cases.
The limiting case predictions we derive serve as baselines to help us interpret results from empirically-based simulations (described below).
We focus on synchrony of per capita growth rates, rather than abundances, because growth rates represent the instantaneous response of species to the environment and competition, and are less susceptible to the legacy effects of drift and disturbance [@Loreau2008a].
We present equivalent results for synchrony of species abundances in the Appendix S1, and show that they lead to the same overall conclusions as synchrony of per capita growth rates.
Following @Loreau2008a and @DeMazancourt2013a, we define population growth, ignoring observation error, as

@@

\noindent where $N_i(t)$ is the biomass of species *i* in year *t*, and $r_i(t)$ is its population growth rate in year *t*. 
$r_{mi}$ is species *i*'s intrinsic rate of increase, $K_i$ is its carrying capacity, and $\alpha_{ij}$ is the interspecific competition coefficient representing the effect of species *j* on species *i*. 
Environmental stochasticity is incorporated as $\sigma_{ei}u_{ei}(t)$, where $\sigma_{ei}^2$ is the environmental variance and $u_{ei}$ are normal random variables with zero mean and unit variance that are independent through time but may be correlated between species.
Demographic stochasticity arises from variations in births and deaths among individuals (e.g., same states, different fates), and is included in the model as a first-order, normal approximation [@Lande2003; @DeMazancourt2013a].
$\sigma_{di}^2$ is the demographic variance and $u_{di}(t)$ are independent normal variables with zero mean and unit variance.
To derive analytical predictions we solved a first-order approximation of Equation 2 [@DeMazancourt2013a and Appendix S1].
Due to the linear approximation approach, our analytical predictions will likely fail in communities where species exhibit large fluctuations due to limit cycles and chaos [@Loreau2008a].
Indeed, one of the advantages of focusing on growth rates rather than abundances is that growth rates are more likely to be well-regulated around an equilibrium value, if the long-term average of a species' growth rate is relatively small (e.g., $r < 2$).

@@

#### Fitting statistical models
Vital rate regressions are the building blocks of our dynamic models: an integral projection model (IPM) and an individual-based model (IBM).
We followed the approach of @Chu2015 to fit statistical models for survival, growth, and recruitment (see Appendix S1 for full details).
We modeled survival probability of each genet as function of genet size, temporal variation among years, permanent spatial variation among groups of quadrats, and local neighborhood crowding from conspecific and heterospecific genets.
Regression coefficients for the effect of crowding by each species can be considered a matrix of interaction coefficients whose diagonals represent intraspecific interactions and whose off-diagonals represent interspecific interactions [@Adler2010]. These interaction coefficients can take positive (facilitative) or negative (competitive) values.
We modeled growth as the change in size of a genet from one year to the next, which depends on the same factors as the survival model.
We fit the survival and growth regressions using INLA [@Rue2014], a statistical package for fitting generalized linear mixed effects models via approximate Bayesian inference [@Rue2009], in R [@R2013].
Crowding was treated as a fixed effect without a temporal component because most 95\% credible intervals for random year effects on crowding broadly overlapped zero and, in a test case, including yearly crowding effects did not change our results.
Spatial (quadrat groupings) variation was treated as a random effect on the intercept and temporal (interannual) variation was treated as random effects on the intercept and the effect of genet size in the previous year (Appendix S1).

@@

For all five communities, the synchrony of species' growth rates when growing in isolation almost perfectly matched species synchrony in polyculture (Fig. 3).
Results for synchrony of percent cover are qualitatively similar, but simulation results were more variable and less consistent with analytical predictions and observed synchrony (Appendix S1, Figs. S2-S3).

DISCUSSION
----------
Our study produced four main findings that were generally consistent across five natural plant communities: (1) limiting-case predictions from the theoretical model were well-supported by simulations from the empirical models; (2) demographic stochasticity decreased community synchrony, as expected by theory, and its effect was largest in small populations; (3) environmental fluctuations increased community synchrony relative to simulations in constant environments because species-specific responses to the environment were positively, though not perfectly, correlated; and (4) interspecific interactions were weak and therefore had little impact on community synchrony.
We also found that analyses based on synchrony of species' percent cover, rather than growth rates, were uninformative (Figs. S2-S3) since the linear approximation required for analytical predictions is a stronger assumption for abundance than growth rates, especially given relatively short time-series (Appendix S1).
Thus, our results provide further evidence that it is difficult to decipher mechanisms of species synchrony from abundance time series, as expected by theory [@Loreau2008a].
Observed synchrony of per capita growth rates was positively correlated with the variability of percent cover across our focal communities, which confirms that we are investigating an important process underlying ecosystem stability.

### 2016-08-12 docs/ms_communitySynchrony.tex
submission version for Ecology

\usepackage{lineno}
\linenumbers
\usepackage{setspace}
\usepackage{todonotes}
\doublespacing
\usepackage{rotating}
\usepackage{color, soul}

@@

@@

Ecosystems are being transformed by species extinctions (Cardinale et
al. 2012), changes in community composition (Vellend et al. 2013,
Dornelas et al. 2014), and anthropogenic environmental change (Vitousek
et al. 1997), impacting the provisioning and stability of ecosystem
services (Loreau et al. 2001, Hooper et al. 2005, Rockstrom et al.
2009). Experiments have provided compelling evidence that decreases in
species richness will decrease productivity (Tilman et al. 2001) and the
temporal stability of productivity (Tilman et al. 2006, Hector et al.
2010). The stabilizing effect of species richness stems from individual
species responding in different way\} to environmental fluctuations
(environmental stochasticity), or fluctuating asynchronously because of
random chance events (demographic stochasticity) (Isbell et al. 2009,
Hector et al. 2010, {{de Mazancourt}} et al. 2013). Species richness
affects synchrony because larger species pools are more likely to
contain species that respond disimilarly to environmental conditions
(Yachi and Loreau 1999), implying that species losses will reduce
ecosystem stability. Even without species losses, abiotic homogenization
can weaken compensatory dynamics and, in turn, decrease temporal
stability of ecosystem functioning (Hautier et al. 2014). The link
between synchrony and stability means that a mechanistic understanding
of synchrony can help us predict the impacts of global change on
ecosystem stability.

@@

While existing theory has identified the factors driving synchrony, we
do not have a simple expression to predict synchrony in a particular
community with all factors operating simultaneously. However, we can
derive analytical predictions for species synchrony under special
limiting cases. The limiting case predictions we derive serve as
baselines to help us interpret results from empirically-based
simulations (described below). We focus on synchrony of per capita
growth rates, rather than abundances, because growth rates represent the
instantaneous response of species to the environment and competition,
and are less susceptible to the legacy effects of drift and disturbance
(Loreau and {{de Mazancourt}} 2008). We present equivalent results for
synchrony of species abundances in the Online Supporting Information,
and show that they lead to the same overall conclusions as synchrony of
per capita growth rates. Following Loreau and {{de Mazancourt}} (2008)
and {{de Mazancourt}} et al. (2013), we define population growth,
ignoring observation error, as

@@

\noindent where \(N_i(t)\) is the biomass of species \emph{i} in year
\emph{t}, and \(r_i(t)\) is its population growth rate in year \emph{t}.
\(r_{mi}\) is species \emph{i}`s intrinsic rate of increase, \(K_i\) is
its carrying capacity, and \(\alpha_{ij}\) is the interspecific
competition coefficient representing the effect of species \emph{j} on
species \emph{i}. Environmental stochasticity is incorporated as
\(\sigma_{ei}u_{ei}(t)\), where \(\sigma_{ei}^2\) is the environmental
variance and \(u_{ei}\) are normal random variables with zero mean and
unit variance that are independent through time but may be correlated
between species. Demographic stochasticity arises from variations in
births and deaths among individuals (e.g., same states, different
fates), and is included in the model as a first-order, normal
approximation (Lande et al. 2003, {{de Mazancourt}} et al. 2013).
\(\sigma_{di}^2\) is the demographic variance and \(u_{di}(t)\) are
independent normal variables with zero mean and unit variance. To derive
analytical predictions we solved a first-order approximation of Equation
2 ({{de Mazancourt}} et al. 2013 and Online Supporting Information). Due
to the linear approximation approach, our analytical predictions will
likely fail in communities where species exhibit large fluctuations due
to limit cycles and chaos (Loreau and {{de Mazancourt}} 2008). Indeed,
one of the advantages of focusing on growth rates rather than abundances
is that growth rates are more likely to be well-regulated around an
equilibrium value, if the long-term average of a species' growth rate is
relatively small (e.g., \(r < 2\)).

@@

Vital rate regressions are the building blocks of our dynamic models: an
integral projection model (IPM) and an individual-based model (IBM). We
followed the approach of Chu and Adler (2015) to fit statistical models
for survival, growth, and recruitment (see Online Supporting Information
for full details). We modeled survival probability of each genet as
function of genet size, temporal variation among years, permanent
spatial variation among groups of quadrats, and local neighborhood
crowding from conspecific and heterospecific genets. Regression
coefficients for the effect of crowding by each species can be
considered a matrix of interaction coefficients whose diagonals
represent intraspecific interactions and whose off-diagonals represent
interspecific interactions (Adler et al. 2010). These interaction
coefficients can take positive (facilitative) or negative (competitive)
values. We modeled growth as the change in size of a genet from one year
to the next, which depends on the same factors as the survival model. We
fit the survival and growth regressions using INLA (Rue et al. 2014), a
statistical package for fitting generalized linear mixed effects models
via approximate Bayesian inference (Rue et al. 2009), in R (R Core Team
2013). Crowding was treated as a fixed effect without a temporal
component because most 95\% credible intervals for random year effects
on crowding broadly overlapped zero and, in a test case, including
yearly crowding effects did not change our results. Spatial (quadrat
groupings) variation was treated as a random effect on the intercept and
temporal (interannual) variation was treated as random effects on the
intercept and the effect of genet size in the previous year (Online
Supporting Information).

@@

For all five communities, the synchrony of species' growth rates when
growing in isolation almost perfectly matched species synchrony in
polyculture (Fig. 3). Results for synchrony of percent cover are
qualitatively similar, but simulation results were more variable and
less consistent with analytical predictions and observed synchrony
(Online Supporting Information, Figs. S2-S3).

@@

Our study produced four main findings that were generally consistent
across five natural plant communities: (1) limiting-case predictions
from the theoretical model were well-supported by simulations from the
empirical models; (2) demographic stochasticity decreased community
synchrony, as expected by theory, and its effect was largest in small
populations; (3) environmental fluctuations increased community
synchrony relative to simulations in constant environments because
species-specific responses to the environment were positively, though
not perfectly, correlated; and (4) interspecific interactions were weak
and therefore had little impact on community synchrony. We also found
that analyses based on synchrony of species' percent cover, rather than
growth rates, were uninformative (Figs. S2-S3) since the linear
approximation required for analytical predictions is a stronger
assumption for abundance than growth rates, especially given relatively
short time-series (Online Supporting Information). Thus, our results
provide further evidence that it is difficult to decipher mechanisms of
species synchrony from abundance time series, as expected by theory
(Loreau and {{de Mazancourt}} 2008). Observed synchrony of per capita
growth rates was positively correlated with the variability of percent
cover across our focal communities, which confirms that we are
investigating an important process underlying ecosystem stability.

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[width=6in]{./components/formatted_figures/formatted_figure1.png}
  \caption{Community-wide species synchrony of per capita growth rates from model simulation experiments. Synchrony of species' growth rates for each study area are from simulation experiments with demographic stochasticity, environmental stochasticity, and interspecific interactions present (``All Drivers''), demographic stochasticity removed (``No D.S.''), environmental stochasticity removed (``No E.S.''), interspecific interactions removed (``No Comp.''), interspecific interactions and demographic stochasticity removed (``No Comp. + No D.S.''), and interspecific interactions and environmental stochasticity removed (``No Comp. + No E.S.''). Abbreviations within the bars for the New Mexico site indicate whether the IBM or IPM was used for a particular simulation. Error bars represent the 2.5\% and 97.5\% quantiles from model simulations. All IBM simulations shown in this figure were run on a 25 $\text{m}^2$ virtual landscape. Points show observed and predicted synchrony aligned with the model simulation that corresponds with each observation or analytical predicion.}
\end{figure}

>>>>

\usepackage{lineno}
\linenumbers
\usepackage{setspace}
\usepackage{todonotes}
\doublespacing
\usepackage{rotating}
\usepackage{color, soul}
\usepackage{times}
\usepackage[document]{ragged2e}

@@

\renewcommand\linenumberfont{\normalfont\tiny\sffamily\color{gray}}

@@

Ecosystems are being transformed by species extinctions (Cardinale et
al. 2012), changes in community composition (Vellend et al. 2013,
Dornelas et al. 2014), and anthropogenic environmental change (Vitousek
et al. 1997), impacting the provisioning and stability of ecosystem
services (Loreau et al. 2001, Hooper et al. 2005, Rockstrom et al.
2009). Experiments have provided compelling evidence that decreases in
species richness will decrease productivity (Tilman et al. 2001) and the
temporal stability of productivity (Tilman et al. 2006, Hector et al.
2010). The stabilizing effect of species richness stems from individual
species responding in different ways to environmental fluctuations
(environmental stochasticity), or fluctuating asynchronously because of
random chance events (demographic stochasticity) (Isbell et al. 2009,
Hector et al. 2010, {{de Mazancourt}} et al. 2013). Species richness
affects synchrony because larger species pools are more likely to
contain species that respond disimilarly to environmental conditions
(Yachi and Loreau 1999), implying that species losses will reduce
ecosystem stability. Even without species losses, abiotic homogenization
can weaken compensatory dynamics and, in turn, decrease temporal
stability of ecosystem functioning (Hautier et al. 2014). The link
between synchrony and stability means that a mechanistic understanding
of synchrony can help us predict the impacts of global change on
ecosystem stability.

@@

While existing theory has identified the factors driving synchrony, we
do not have a simple expression to predict synchrony in a particular
community with all factors operating simultaneously. However, we can
derive analytical predictions for species synchrony under special
limiting cases. The limiting case predictions we derive serve as
baselines to help us interpret results from empirically-based
simulations (described below). We focus on synchrony of per capita
growth rates, rather than abundances, because growth rates represent the
instantaneous response of species to the environment and competition,
and are less susceptible to the legacy effects of drift and disturbance
(Loreau and {{de Mazancourt}} 2008). We present equivalent results for
synchrony of species abundances in the Appendix S1, and show that they
lead to the same overall conclusions as synchrony of per capita growth
rates. Following Loreau and {{de Mazancourt}} (2008) and {{de
Mazancourt}} et al. (2013), we define population growth, ignoring
observation error, as

@@

\noindent where \(N_i(t)\) is the biomass of species \emph{i} in year
\emph{t}, and \(r_i(t)\) is its population growth rate in year \emph{t}.
\(r_{mi}\) is species \emph{i}`s intrinsic rate of increase, \(K_i\) is
its carrying capacity, and \(\alpha_{ij}\) is the interspecific
competition coefficient representing the effect of species \emph{j} on
species \emph{i}. Environmental stochasticity is incorporated as
\(\sigma_{ei}u_{ei}(t)\), where \(\sigma_{ei}^2\) is the environmental
variance and \(u_{ei}\) are normal random variables with zero mean and
unit variance that are independent through time but may be correlated
between species. Demographic stochasticity arises from variations in
births and deaths among individuals (e.g., same states, different
fates), and is included in the model as a first-order, normal
approximation (Lande et al. 2003, {{de Mazancourt}} et al. 2013).
\(\sigma_{di}^2\) is the demographic variance and \(u_{di}(t)\) are
independent normal variables with zero mean and unit variance. To derive
analytical predictions we solved a first-order approximation of Equation
2 ({{de Mazancourt}} et al. 2013 and Appendix S1). Due to the linear
approximation approach, our analytical predictions will likely fail in
communities where species exhibit large fluctuations due to limit cycles
and chaos (Loreau and {{de Mazancourt}} 2008). Indeed, one of the
advantages of focusing on growth rates rather than abundances is that
growth rates are more likely to be well-regulated around an equilibrium
value, if the long-term average of a species' growth rate is relatively
small (e.g., \(r < 2\)).

@@

Vital rate regressions are the building blocks of our dynamic models: an
integral projection model (IPM) and an individual-based model (IBM). We
followed the approach of Chu and Adler (2015) to fit statistical models
for survival, growth, and recruitment (see Appendix S1 for full
details). We modeled survival probability of each genet as function of
genet size, temporal variation among years, permanent spatial variation
among groups of quadrats, and local neighborhood crowding from
conspecific and heterospecific genets. Regression coefficients for the
effect of crowding by each species can be considered a matrix of
interaction coefficients whose diagonals represent intraspecific
interactions and whose off-diagonals represent interspecific
interactions (Adler et al. 2010). These interaction coefficients can
take positive (facilitative) or negative (competitive) values. We
modeled growth as the change in size of a genet from one year to the
next, which depends on the same factors as the survival model. We fit
the survival and growth regressions using INLA (Rue et al. 2014), a
statistical package for fitting generalized linear mixed effects models
via approximate Bayesian inference (Rue et al. 2009), in R (R Core Team
2013). Crowding was treated as a fixed effect without a temporal
component because most 95\% credible intervals for random year effects
on crowding broadly overlapped zero and, in a test case, including
yearly crowding effects did not change our results. Spatial (quadrat
groupings) variation was treated as a random effect on the intercept and
temporal (interannual) variation was treated as random effects on the
intercept and the effect of genet size in the previous year (Appendix
S1).

@@

For all five communities, the synchrony of species' growth rates when
growing in isolation almost perfectly matched species synchrony in
polyculture (Fig. 3). Results for synchrony of percent cover are
qualitatively similar, but simulation results were more variable and
less consistent with analytical predictions and observed synchrony
(Appendix S1, Figs. S2-S3).

@@

Our study produced four main findings that were generally consistent
across five natural plant communities: (1) limiting-case predictions
from the theoretical model were well-supported by simulations from the
empirical models; (2) demographic stochasticity decreased community
synchrony, as expected by theory, and its effect was largest in small
populations; (3) environmental fluctuations increased community
synchrony relative to simulations in constant environments because
species-specific responses to the environment were positively, though
not perfectly, correlated; and (4) interspecific interactions were weak
and therefore had little impact on community synchrony. We also found
that analyses based on synchrony of species' percent cover, rather than
growth rates, were uninformative (Figs. S2-S3) since the linear
approximation required for analytical predictions is a stronger
assumption for abundance than growth rates, especially given relatively
short time-series (Appendix S1). Thus, our results provide further
evidence that it is difficult to decipher mechanisms of species
synchrony from abundance time series, as expected by theory (Loreau and
{{de Mazancourt}} 2008). Observed synchrony of per capita growth rates
was positively correlated with the variability of percent cover across
our focal communities, which confirms that we are investigating an
important process underlying ecosystem stability.

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[width=6in]{./components/formatted_figures/formatted_figure1.png}
  \caption{Community-wide species synchrony of per capita growth rates from model simulation experiments. Synchrony of species' growth rates for each study area are from simulation experiments with demographic stochasticity, environmental stochasticity, and interspecific interactions present (``All Drivers''), demographic stochasticity removed (``No D.S.''), environmental stochasticity removed (``No E.S.''), interspecific interactions removed (``No Comp.''), interspecific interactions and demographic stochasticity removed (``No Comp. + No D.S.''), and interspecific interactions and environmental stochasticity removed (``No Comp. + No E.S.''). Abbreviations within the bars for the New Mexico site indicate whether the IBM or IPM was used for a particular simulation. Error bars represent the 2.5\% and 97.5\% quantiles from model simulations. All IBM simulations shown in this figure were run on a 25 $\text{m}^2$ virtual landscape. Points show observed and predicted synchrony aligned with the model simulation that corresponds with each observation or analytical prediction.}
\end{figure}

### 2016-08-12 docs/online_supporting_information.Rmd
submission version for Ecology

---
layout: 12pt
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{setspace}
   - \usepackage{todonotes}
   - \usepackage{color}
   - \usepackage{rotating}
   - \usepackage{morefloats}
bibliography: ~/Dropbox/Bibliography/CommunitySynchrony.bib
csl: components/ecology.csl

>>>>

---
layout: 12pt
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{setspace}
   - \usepackage{todonotes}
   - \usepackage{color}
   - \usepackage{rotating}
   - \usepackage{morefloats}
   - \usepackage{times} 
   - \usepackage[document]{ragged2e}
bibliography: ~/Dropbox/Bibliography/CommunitySynchrony.bib
csl: components/ecology.csl
